### 2014-03-14 src/analysis.Rnw
udpate

\begin{figure*}[t]
<<op.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.opsel <- o.op.processed
o.xp.opsel <- colnames(o.xp.opsel)[]
colnames(o.xp.opsel)[colnames(o.xp.opsel)=="power"] <- "num.operators"

>>>>

\begin{figure*}[t]
<<op.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.opsel <- o.op.processed
colnames(o.xp.opsel)[colnames(o.xp.opsel)=="power"] <- "num.operators"
